An Online Visual Loop Closure Detection Method for Indoor Robotic Navigation

### 2014-12-01 latex-spie/article.tex
Abstract and Real-Time performance is finished

\begin{abstract}
Visual loop closure detection problem is an active area especially for the indoor environments, where the global position information is missing and the localization information is highly dependent on odometry sensors. In this paper, we propose an enhanced loop closure method based on unsupervised visual landmark extraction with saliency detection technique. In contradistinction to the previous methods, our approach uses additional depth information. Saliency regions are used to refer to the certain distinctive areas on the image patches. They are also suitable to represent locations in a sparse manner.  In order to find out the similarity between two locations we use a straightforward function, that contains the detection confidences of the image and the landmark coordinates in 3D. Recognition of the previously visited and unvisited locations is also considered in the framework. Exemplary results and the practical implementation of the method are also given with the data gathered on the testbed with a depth camera (Kinect) mounted differential drive autonomous ground vehicle. Specifically, we adopt visual place recognition to close loops that is useful for the process of correctly identifying a previously visited location. The algorithm is tested in three different datasets which lighting conditions are different from each other. Additional depth information beside the actual image increases the detection rate especially in dark. 
\end{abstract}

\keywords{Loop closure, depth map, zernike moments,  computer vision}

@@

In mobile robotics, autonomous navigation is an active research area especially for the indoor environments, where the global position information is missing and the localization information is highly dependent on odometry sensors. One of the major problems connected to robotic navigation is Simultaneous localization and mapping (SLAM) which still remains as an assertive problem in a lot of ways. Loop closing is defined as the correct identification of previously visited location in terms of SLAM. Information that is gathered from various data sources including LIDARs, RADARs, stereo and monocular cameras\cite{williams08iros, 5650234} is highly utilized in loop closure detection. With the recent development of visual sensor technologies, the loop closure detection became a problem that is open for research in the field of computer vision.

@@

The method implemented in this paper has been evaluated on three datasets which lighting conditions are different from each other. The tests are done with either using gray and depth images separately or using both of them. After that, the difference matrices are calculated to examine the results. Nearest Neighbour (NN) algorithm is applied to classify the new locations using the $L_{1}$ distance metric. In addition to this, the last 100 sequential frames are not involved in classification phase, because it is assumed that the sensor is always moving and these frames correspond to the just behind of the sensor.

@@

@@

Most of image-to-image loop closure techniques are void of computational efficient. There exist limited number of techniques that operates in real-time without parallelization. The speed tests are done with a MacBook Pro 7,1 which specifications are Intel Core 2 Duo 2.4 GHz CPU. In this setting, the extraction of Quantized Local Zernike Moments of an image of size $256\times 192$ pixels takes approximately $10ms$. The NN classification is applied with simple brute-force searching in which the algorithmic complexty is $\mathcal{O}(mn)$ that depends on the number of frames to compare with. In other words, the amount of time needed to performs this search increases throughout the trajectory. Therefore, the total processing time including the brute force search is $14ms$ in average.

>>>>

\begin{abstract}
In this paper, we present an enhanced loop closure method based on image-to-image matching  relies on Quantized Local Zernike Moments. In contradistinction to the previous methods, our approach uses additional depth information to extract Zernike Moments in local manner. These moments are used to represent holistic shape information inside the image. The complex moments that are extracted from both gray and depth images are coarsely quantized. In order to find out the similarity between two locations, Nearest Neighbour classification algorithm is performed. Examplary results and the practical implementation case of the method are also given with the data gathered on the testbed using a Kinect. The method is evaluated in three different datasets of different lighting conditions. Additional depth information beside the actual image increases the detection rate especially in dark. The results are referred as a successful, high-fidelity online method for visual place recognition as well as to close navigation loops, which is a crucial information for the well known Simultaneously Localization and mapping (SLAM) problem. This technique is quite simple because of its low computational complexity, and performs in real-time with high loop closing accuracy.

\end{abstract}

\keywords{Loop closure, Zernike Moments, image processing, SLAM, depth map, indoor navigation}

@@

In mobile robotics, autonomous navigation is an active research area especially for the indoor environments, where the global position information is missing and the localization information is highly dependent on odometry sensors. One of the major problems linked to robotic navigation is SLAM which still remains as an assertive problem in a lot of ways. Loop closing is defined as the correct identification of previously visited location in terms of SLAM. Information that is gathered from various data sources including LIDARs, RADARs, stereo and monocular cameras\cite{williams08iros, 5650234} is highly utilized in loop closure detection. With the recent development of visual sensor technologies, the loop closure detection became a problem that is open for research in the field of computer vision.

@@

The method implemented in this paper has been evaluated on three datasets which lighting conditions are different from each other. The tests are done with either using gray and depth images separately or using both of them. After that, the difference matrices are calculated to examine the results. Nearest Neighbour (NN) algorithm is applied to classify the new locations using the $L_{1}$ distance metric. In addition to this, the last 100 frames are not included in the classification phase, because it the sensor is always moving and these frames correspond to the area behind the sensor.

@@

As it can be seen in Figure \ref{subfig:pr_bright}

@@

There exist limited number of techniques that operate in real-time without parallelization. The speed tests are done with a MacBook Pro 7,1 which specifications are Intel Core 2 Duo 2.4 GHz CPU. In this setting, the extraction of Quantized Local Zernike Moments of an image of size $256\times 192$ pixels takes approximately $10ms$. The NN classification is applied with simple brute-force searching in which the algorithmic complexity is $\mathcal{O}(mn)$ that depends on the number of frames to compare with. In other words, the amount of time needed to performs this search increases throughout the trajectory. Therefore, the total processing time including the brute force search is $14ms$ in average when approximately 2000 frames are processed.
